### 2022-09-12 dissertation/chapters/01-introduction.tex
📝 (review): First set of changes

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
In recent years, \ac{ML} research has seen some notable achievements in the
academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014,
ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016,
ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown
tremendously over the past decade with successes like AlphaGo, which set new
standards for \ac{AI} capabilities by beating the world's best Go player, Lee
Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo,
called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latyn word
meaning to learn from no prior knowledge} and managed to beat AlphaGo, 100-1
\cite{ref:silver:2017}.

@@

Over the past few years, modern hardware capabilities have improved to the
point where workloads in the field of \ac{ML} that were previously computationally
infeasible, is now possible. One such subfield of \ac{ML} is \acp{ANN}. With
the improvement of hardware came an influx of \ac{ML} researchers that focussed
their attention on the training and generalisation capabilities of \acp{ANN}.

A popular field of focus for studing \acp{ANN} is the training process by which
these models are trained. Today, the most common form of training is
\index{supervised training}supervised learning of \acp{FFNN}, a specific type of
\ac{ANN} \cite{ref:reed:1999}. Training of \acp{ANN} is seen as an optimisation problem.
A search algorithm known as a \index{heuristic}\textit{heuristic}
\cite{ref:pearl:1984} is used to assign the optimal values to the \ac{ANN}
weights such that a specified objective function is minimised.

Although the landscape of what can be solved using \acp{ANN} today
is extensive, there still exists no single model that can be generalised to
solving multiple problem classes, across multiple problem domains. This problem
is known as the \ac{NFL} \cite{ref:wolpert:1997}.

Various attempts have been made to improve the generalisation capabilities of
\acp{ANN}. Examples of techniques used include weight \index{dropout}dropout
\cite{ref:srivastava:2014}, \index{weight decay}weight decay
\cite{ref:krogh:1992}, \index{meta-learning}meta-learning of learning parameters
such as the \index{learning rate}learning rate and \index{momentum}momentum of
gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992}
and carefully selecting training data. Other techniques focus on improving
generalisation through model design (architecture and topology). Examples of such
techniques include learning of \ac{ANN} architectures through pruning techniques
\cite{ref:cibas:1996, ref:engelbrecht:1996} or constructive techniques
\cite{ref:hassibi:1994, ref:lecun:1990}, adaptive activation functions
\cite{ref:engelbrecht:1995, ref:fletcher:1994}, and quantum methods
\cite{ref:wan:2017, ref:ricks:2004}.

One promising approach to improving \ac{ANN} generalisation capabilities is the
idea of hybridisation \cite{ref:burke:2013}, which makes use of a combination of
multiple learning paradigms in order to yield better generalisation. For
example, heteregenous approaches have been shown to balance the tradeoff between
exploration and exploitation. \cite{ref:nepomuceno:2013}. This hints towards the
idea that \ac{ML} models could yield better generalisation capabilities if the
learning process and learning mechanism applied is not statically defined, but
rather dynamic and under the control of some control mechanism.

The learning process is influenced by various factors, including the type of
learning technique used, how the model parameters are initialised, the
hyper-parameters used, the constraints of learning and the learning mechanism
itself. In order to yield better generalisation capabilities, the model should
be trained by a learning technique that has at its disposal a more diverse set
of learning behaviours from which it can dynamically select should the need arise
\cite{ref:huang:2009}. In doing so, balancing between exploration and
exploitation of solutions is a dynamic process that would yield better
generalisation capabilities.

An example of dynamically balancing exploitation and exploration during the
search process is done by dynamically adjusting and learning the heuristic
\index{hyper-parameters}\textit{hyper-parameters} as part of the learning
process. This field of study is known as \index{meta-learning}meta-learning
\cite{ref:giraud:2004}. \index{meta-learning}Meta-learning of heuristic
hyper-parameters as applied in the training of \acp{ANN} has shown to yield good
generalisation results \cite{ref:hospedales:2020, ref:vilalta:2002}.

A more recent suggestion related to the field of
\index{meta-learning}meta-learning is to dynamically select and/or adjust the
heuristic used throughout the training process. This approach is about the
hybridisation of heuristics as they are applied to some optimisation problem.
These methods are referred to as \acp{HH} and focus on finding the best
heuristic in \textit{heuristic-space}. One such form of \ac{HH} is a
population-based approach that guides the search process by automatically
selecting heuristics from a heuristic-space to be applied to a collection of
different candidate solutions in the solution-space. This collection of
candidate solutions are referred to as a \textit{population} of
\textit{entities}, where each \textit{entity} is a single candidate solution to
the problem being optimised.

Population-based \acp{HH} implement the strategy of multiple heuristics working
together to solve a problem. However, finding the best heuristic to use is
non-trivial and some \textit{selection strategy} must be used to select the best
heuristic. \acp{HH} that implement such a selection strategy is referred to as
\textit{selection} \acp{HH}. The term \textit{selection} refers to the ability
of the \ac{HH} to select the best heuristic from a pool of low-level heuristics.

@@

This thesis focusses on the development of a \ac{HH} to train \acp{FFNN} in a
supervised learning approach.

@@

Many different heuristics have been developed and used to train \acp{FFNN}
\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.  The problem
lies in the process of finding the best heuristic to train the \ac{FFNN}. This
process is often non-trivial and could be a time-consuming exercise.  Consider
that selection of the best heuristic as applied to optimisation problems, such
as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996,
ref:drake:2020, ref:pillay:2018}. Furthermore, the \ac{NFL} shows that no single
heuristic performs better than any other heuristic for all problems
\cite{ref:wolpert:1997}.

Careful, systematic selection is thus required to find and select the best
heuristic to train \acp{FFNN}. In the past, researchers selected the best
heuristic by trail and error. A set of heuristics and carefully selected
hyper-parmeters would be implemented, followed by an empirical test to evaluate
the performance of each heuristic for a given problem domain
\cite{ref:pillay:2015}. In this way, researchers were able to determine which
heuristics and which hyper-parameters performed well for different problems.
However, this approach is problematic as it is time-consuming and tedious.

@@

A modern approach is to use \acp{HH} to automated the process for selecting the
best heuristic when applied to some optimisation problem. The best heuristic
might not be a single heuristic, but rather a hybridisation of heuristics
\cite{ref:pillay:2015}. Therefore, careful consideration is required to include
a diverse and applicable set of heuristics to select from that is capable of
solving the given problem. \citeauthor{ref:pillay:2015} \cite{ref:pillay:2015}
mentions that only heuristics that are known to have the potential to solve the
problem must be included in the set of heuristics to select from.

\acp{HH} have been implemented on a wide range of optimisation problems
\cite{ref:grobler:2011, ref:burke:2013, ref:pillay:2015}, but no research has
been found where \acp{HH} have been applied on the training of \acp{FFNN}.

The training of \acp{FFNN} is seen as a computational search problem. \Acl{HH}
as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or
learning mechanism for selecting or generating heuristics to solve computational
search problems". \acp{HH} is a field of research aimed at the automated
selection, combination, adaptation and generation of multiple lower-level
heuristics to efficiently solve computational search problems. This implies that
one should be able to apply \acp{HH} in the context of training \acp{FFNN}.

\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mentions that the focus of
\acp{HH} is on automating the development of the \textit{learning mechanism}
used to obtain an appropriate solution for an optimisation problem. The authors
go on to explain that \acp{HH} employ a high-level heuristic that focusses on
finding the best low-level heuristic in heuristic-space that could include
\textit{single-method} and \textit{multi-method} optimistion algorithms
(heuristics). Applying \acp{HH} to train \acp{FFNN} could generally be applied
to multiple problems given that the set of low-level heuristics include
heuristics that have the potential to solve the problem at hand
\cite{ref:burke:2010}. This relieves the burden of having to select the best
heuristic to use by trial and error and is generally applicable to multiple
problems. The automation of the selection process as well as the generalisation
capabilities of \acp{HH}, if applied in the context of training \acp{FFNN},
could reduce the effort required to find the best heuristic to use.

Note that training \acp{FFNN} using \acp{HH} is not to be confused by the
training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks}
or \index{query by committees}\textit{query by committees}.
\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describes \index{ensemble
networks}ensemble networks as a combination method in
\index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used
to solve a problem. Each member network in the ensemble gets trained using a
specified heuristic and generally this heuristic is applied to the same member
throughout the training process. The results of all of the member networks are
then joined together using some mechanism \cite{ref:zhou:2002}. This mechanism
could be weighted averages or majority or weighted voting. \index{ensemble
networks}Ensemble networks do not search through the heuristic space and do not
reselect lower-level heuristics for each member, while \acp{HH} do. There is
thus no hybridisation of heuristics in \index{ensemble networks}ensemble
networks and therefore, no information-sharing between any of the members of the
ensemble, in comparison to \acp{HH} that do incorporate some shared information
space.

Many different types of \acp{HH} have been implemented and shown to solve many
different problems. Some notable examples include the
\index{tabu-search}tabu-search \ac{HH} of Burke et al. \cite{ref:burke:2010} and
the \index{simulated annealing}simulated annealing-based \ac{HH} by Dowsland et
al. \cite{ref:dowsland:2007}.

This research takes a particular interest in developing a high-level heuristic
that makes use of probability theory and Bayesian statistical concepts to guide
the heuristic selection process. This research develops the novel \Ac{BHH}, a
new high-level heuristic that utilises \index{Bayesian analysis}\textit{Bayesian
analysis} as the selection mechanism for a \ac{HH} to select the appropriate
heuristic to train \acp{FFNN}.

@@

The main objectives of this research is focussed on developing a novel \Ac{BHH}
selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
In order to reach this objective, the following sub-objectives are defined:

@@

    \item
    Conduct a literature study on different types of heuristics that have been
    used to train \acp{FFNN}. The literature study will provide the necessary
    background information to understand how the these different heuristics can
    be used in the set of heuristics to be selected to train the \ac{FFNN}.

@@

@@

    \item
    Conduct an empirical study and critically evaluate the performance of the
    developed \Ac{BHH} as a selection mechanism to other selection mechanisms
    for \acp{HH} as they are used to train \acp{FFNN} on different problems.

    \item
    Conduct an empirical study that investigate variations of the \Ac{BHH} and the
    effects of design decisions and hyper-parameters on the search process.

@@

The results obtained from this research contributes to the field of study in the
following ways:

\begin{itemize}
    \item
    To the knowledge of the author, this study provides the first application
    of using \acp{HH} to train \acp{FFNN}.

    \item
    A novel heuristic selection operator is used that focusses on using Bayesian
    statistics to calculate the probability that a heuristic should be selected
    in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred
    to as the \Acl{BHH}.

    \item
    The results of the empirical study show that the \Ac{BHH} perform generally
    better than the individual lower-level heuristics as applied to the same
    problems, with statistical significance and certainty.

@@

    \item
    The results of the empirical study show that the \Ac{BHH}, given a diverse
    set of lower-level heuristics, will generally produce good results when
    applied to multiple problems.

    \item
    Finally, the results of the empirical study show that the \Ac{BHH} is
    capable of utilising \textit{a priori} \footnote{Latin word, meaning "from
    what comes before"} knowledge in which a predefined selection bias is used
    for heuristics the are known to be well suited for certain problems.
\end{itemize}

\section{Thesis Outline}
 \label{sec:introduction:outline}

The remainder of this thesis is structured as follows:

 \begin{itemize}
 	\item
    \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN}
    and the various components that make up an \ac{AN}. The focus is on the
    training of \acp{FFNN} and it is shown how the training of \acp{FFNN} is
    seen as an optimisation problem.

	\item
    \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of
    heuristics and metaheuristics that have been used to train \acp{FFNN}. A
    literature study is done to provide details on the search behaviours, application and
    implementation of each heuristics in the context of training \acp{FFNN}.

	\item
    \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details
    of \acp{HH} and \index{meta-learning}meta-learning in general. A
    discussion follows on the current landscape of \ac{HH} research. It is shown
    how \acp{HH} is a suitabe approach for training \acp{FFNN}.

    \item
    \textbf{Chapter~\ref{chap:probability}} presents a literature study on
    probability theory. Probability distributions and
    conjugate priors are discussed in detail. The chapter concludes with a
    detailed discussion on Bayesian statistics, specifically focussing on
    Bayesian inference and analysis.

@@

	\item
    \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of
    the empirical process and the setup of each experiment. It discusses the
    datasets used, the \ac{FFNN} architecture and topology used, heuristics that
    are used, the configuration of hyper-parameters, initialisation techniques
    used, performance measures used and other smaller details to the
    implementation of each experiment.  Finally discussions follow on how the
    results are analysed. This includes a discussion on the method used to
    determine statistical significance.

@@

	\item
    \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this
    thesis along with a brief overview of findings made throughout the research
    process. A review of the research goals are given and suggestions for future
    research are made.
\end{itemize}

This thesis is accompanied by a full index given at page~\pageref{index} along with the following appendices:

@@

@@

 	\item
    \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical
    symbols used in this work, categorised according to the relevant chapter
    in which they appear.

 	\item
    \textbf{Appendix~\ref{app:derived_publications}} lists the publications
    derived from this work.
 \end{itemize}

To best view the illustrations, tables and figures presented throughout this
thesis, it is recommended that the thesis be viewed in colour.

>>>>

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
In recent years, \ac{ML} research has seen some notable achievements in the
academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014,
      ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016,
      ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown
tremendously over the past decade with successes like AlphaGo, which set new
standards for \ac{AI} capabilities by beating the world's best Go player, Lee
Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo,
called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word
      meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1
\cite{ref:silver:2017}.

@@

Over the past few years, modern hardware capabilities have improved to the
point where workloads in the field of \ac{ML} that were previously computationally
infeasible, are now possible. One such sub-field of \ac{ML} is \acp{ANN}. \acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}. \acp{ANN} are the digital equivalent of how we currently understand the brain to work. \acp{ANN} can be trained, which is the equivalent of ``learnin'' from data. Learning gives rise to the ability to apply some form of decision making. This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field. With the improvement of hardware came an influx of \ac{ML} researchers that focused
their attention on the training of \acp{ANN}.

A popular field of focus for studying \acp{ANN} is the process by which
these models are trained. \acp{FFNN} are specific types of
\acp{ANN} \cite{ref:reed:1999}. The most common way of training \acp{FFNN} is
\index{supervised training}supervised learning. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic}
\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.

Although the landscape of what can be solved using \acp{ANN} today
is extensive, there still exists no single model that can be generalised to
solving multiple problem classes, across multiple problem domains. \acs{ANN} training algorithms mostly yield problem specific solutions. This means that a particular approach that works well for one domain of problem class, often does not necessarily work for another. This problem is known as the \ac{NFL} \cite{ref:wolpert:1997}.

Generalisation of \acp{ANN} refer to the capabilities of the network to either perform well on unseen data or to be applied to other problem domains. Various attempts have been made to improve the generalisation capabilities of
\acp{ANN}. Examples of techniques used include weight \index{dropout}dropout
\cite{ref:srivastava:2014}, \index{weight decay}weight decay
\cite{ref:krogh:1992}, \index{meta-learning}meta-learning of learning parameters
such as the \index{learning rate}learning rate and \index{momentum}momentum of
gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992},
and removing or postponing the use of outliers in the training data \cite{ref:reeves:1998}. Other techniques focus on improving
generalisation through model design. Design configurations focus on the layout of the neurons and structure of the \acs{ANN} (architecture) and how neurons are connected to interact (topology). Examples of such
techniques include learning of \ac{ANN} architectures through pruning techniques
\cite{ref:cibas:1996, ref:engelbrecht:1996} or constructive techniques
\cite{ref:hassibi:1994, ref:lecun:1990}, adaptive activation functions
\cite{ref:engelbrecht:1995, ref:fletcher:1994}, and quantum methods
\cite{ref:wan:2017, ref:ricks:2004}.

The performance and capabilities of \acp{ANN} is largely influenced by the learning process used. The learning process consists of multiple components. These include the type of underlying optimisation algorithm used, how the model parameters are initialised, the hyper-parameters used and the constraints of learning such as allowed search space and boundaries. Each of these elements influence how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.

An example of dynamically balancing exploitation and exploration during the
search process is by dynamically adjusting and learning the heuristic
\index{hyper-parameters}\textit{hyper-parameters} as part of the learning
process. This field of study is known as \index{meta-learning}meta-learning
\cite{ref:giraud:2004}. \index{meta-learning}Meta-learning of heuristic
hyper-parameters as applied in the training of \acp{ANN} has shown to yield good
generalisation results \cite{ref:hospedales:2020, ref:vilalta:2002}.

This dynamic nature of the learning process leads towards the
idea that \ac{ML} models could yield better generalisation capabilities if the
learning process and learning mechanism applied are not statically defined, but
rather dynamic and under the control of some mechanism. Furthermore, a learning technique that has at its disposal a more diverse set
of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.

A more recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process. This approach focuses on the hybridisation of learning paradigms. The main concept behind this paradigm is that the learning process is dynamic and differs from problem to problem. A particular learning technique might work well for one problem and not for another. At the same time, a particular learning technique might work well for a particular part of the search landscape, but not for another. By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between exploration and exploitation as is required.

One such form of hybridisation of learning paradigms is referred to as \index{heterogeneous learning approaches}\textit{heterogeneous learning approaches}. Heterogeneous learning approaches make use of different search behaviours by selecting from a behaviour pool. Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation \cite{ref:nepomuceno:2013}.

A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different heuristics as they are applied to some optimisation problem \cite{ref:burke:2013}. These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic-space} to solve a specific problem. One such form of \ac{HH} is a
population-based approach that guides the search process by automatically
selecting heuristics from a heuristic-space to be applied to a collection of
different candidate solutions in the solution-space. This collection of
candidate solutions are referred to as a \textit{population} of
\textit{entities}, where each \textit{entity} is a single candidate solution to
the problem being optimised.

Population-based \acp{HH} implement the strategy of multiple heuristics working
together to solve a problem. However, finding the best heuristic to use is
non-trivial and some \textit{selection strategy} must be used to select the best
heuristic. \acp{HH} that implement such a selection strategy are referred to as
\textit{selection} \acp{HH}. The term \textit{selection} refers to the ability
of the \ac{HH} to select the best heuristic from a pool of low-level heuristics.

@@

This dissertation focuses on the development of a \ac{HH} to train \acp{FFNN} in a
supervised learning approach.

@@

Many different heuristics have been developed and used to train \acp{FFNN}
\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \ac{FFNN} is required in order to yield optimal results. This
process is often non-trivial and could be a time-consuming exercise.  Consider
that selection of the best heuristic as applied to optimisation problems, such
as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996,
      ref:drake:2020, ref:pillay:2018}.

Careful, systematic selection is thus required to find and select the best
heuristic to train \acp{FFNN}. In the past, researchers selected the best
heuristic by trail and error. A set of heuristics and carefully selected
hyper-parameters would be implemented, followed by an empirical test to evaluate
the performance of each heuristic for a given problem domain
\cite{ref:pillay:2015}. In this way, researchers were able to determine which
heuristics and which hyper-parameters performed well for different problems.
However, this approach is problematic, because it is time-consuming and tedious.

@@

A modern approach is to use \acp{HH} to automate the process of selecting the
best heuristic when applied to some optimisation problem. The best heuristic
might not be a single heuristic, but rather a hybridisation of heuristics
\cite{ref:pillay:2015}. Therefore, careful consideration is required to include and select from a diverse set of heuristics that is capable of solving the given problem. Importantly, only heuristics that are known to have the potential to solve the
problem are applicable and can be included in the set of heuristics to select from.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many
different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce. \citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The shortage of research in this field certainly warrants more exploration.

\acp{FFNN} training is seen as a computational search problem. \Acl{HH}
as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or
learning mechanism for selecting or generating heuristics to solve computational
search problems''. \acp{HH} is a field of research aimed at the automated
selection, combination, adaptation or generation of multiple lower-level
heuristics to efficiently solve computational search problems. This implies that
it should be possible to apply \acp{HH} in the context \acs{FFNN} training.

\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mention that the focus of
\acp{HH} is on automating the development of the \textit{learning mechanism}
used to find the best heuristic to obtain an appropriate solution to an optimisation problem. \citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on
finding the best low-level heuristic in heuristic-space that could include
\textit{single-method} and \textit{multi-method} optimisation algorithms
(heuristics). \acp{HH} relieve the burden of having to select the best
heuristic to use by trial and error. Furthermore, \acp{HH} can generally be applied to multiple
problems given that the set of low-level heuristics include
heuristics that have the potential to solve the problem at hand
\cite{ref:burke:2010}. Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of \acp{FFNN} training.

Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the
training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks}
or \index{query by committees}\textit{query by committees}.
\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describe \index{ensemble
      networks}ensemble networks as a combination method in
\index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used
to solve a problem. Each member network in the ensemble is trained using a
specified heuristic, and generally this heuristic is applied to the same member
throughout the training process. The results of all of the member networks are
then joined together using some consensus mechanism \cite{ref:zhou:2002}. This mechanism
could be weighted averages, majority voting or weighted voting. \index{ensemble
      networks}Ensemble networks do not search through the heuristic space to find the best training algorithm for each member, while \acp{HH} do.

This research takes a particular interest in developing a high-level heuristic
that makes use of probability theory and Bayesian statistical concepts to guide
the heuristic selection process. This research develops the novel \Acf{BHH}, a
new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian
      analysis} which combines prior information with new evidence to the parameters of a selection probability distribution. This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate
heuristics to train \acp{FFNN} during the training process (online learning).

@@

The main objective of this research is focused on developing a novel \Ac{BHH}
selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
In order to reach this objective, the following sub-objectives are defined:

@@

      \item
            Conduct a literature study on different types of heuristics that have been
            used to train \acp{FFNN}. The literature study will provide the necessary
            background information to understand how these different heuristics can
            be used in the set of heuristics to be selected to train the \ac{FFNN}.

@@

      \item Conduct an empirical study to investigate the behavioural characteristics of the \ac{BHH} as it is used to train \acp{FFNN} over a number of different datasets.

@@

      \item
            Conduct an empirical study that investigates variations of the \Ac{BHH} and the
            effects of design decisions and hyper-parameters on the search process.

@@

The results obtained from this research contribute to the field of study in the
following ways:

\begin{itemize}
      \item
            A novel heuristic selection operator is used that focuses on using Bayesian
            statistics to calculate the probability that a heuristic should be selected
            in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred
            to as the \Acl{BHH}.

      \item
            The results of the empirical study show  with statistical significance and certainty that the \Ac{BHH} performs generally
            well on multiple problems. It is shown that, for each problem, the \Ac{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.

@@

      \item
            The results of the empirical study show that the \Ac{BHH}, given a diverse
            set of lower-level heuristics, will generally produce good results when
            applied to multiple problems at the same time.

      \item
            Finally, the results of the empirical study show that the \Ac{BHH} is
            capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from
                  what comes before''.} knowledge in which a predefined selection bias is used
            for heuristics that are known to be well suited for certain problems.
\end{itemize}

\section{Dissertation Outline}
\label{sec:introduction:outline}

The remainder of this dissertation is structured as follows:

\begin{itemize}
      \item
            \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN}
            and the various components that make up an \acl{AN}. The focus is on the
            training of \acp{FFNN}. It is shown how the training of \acp{FFNN} is
            seen as an optimisation problem.

      \item
            \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of
            heuristics and meta-heuristics that have been used to train \acp{FFNN}. A
            literature study is done to provide details on the search behaviours, application and
            implementation of each heuristic in the context of training \acp{FFNN}.

      \item
            \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details
            of \acp{HH} and \index{meta-learning}meta-learning in general. A
            discussion follows on the current landscape of \ac{HH} research and a review of different selection approaches for \acp{HH} is conducted. It is shown how \acp{HH} are suitable for \acs{FFNN} training.

      \item
            \textbf{Chapter~\ref{chap:probability}} presents a literature study on
            probability theory. Probability distributions and
            conjugate priors are discussed in detail. The chapter concludes with a
            detailed discussion on Bayesian statistics, specifically focusing on
            Bayesian inference and analysis.

@@

      \item
            \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of
            the empirical process and the setup of each experiment. It discusses the
            datasets used, the \ac{FFNN} architecture and topology used, heuristics that
            are used, the configuration of hyper-parameters, initialisation techniques
            used, performance measures used and other smaller details of the
            implementation of each experiment.  Finally, discussions follow on how the
            results are analysed. This includes a discussion on the method used to
            determine statistical significance.

@@

      \item
            \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this
            dissertation along with a brief overview of the findings made throughout the research
            process. A review of the research goals are given and suggestions for future
            research are made.
\end{itemize}

This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:

@@

      \item
            \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.

@@

      \item
            \textbf{Appendix~\ref{app:derived_publications}} lists the publications
            derived from this work.

      \item
            \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical
            symbols used in this work, categorised according to the relevant chapter
            in which they appear.
\end{itemize}

To best view the illustrations, tables and figures presented throughout this
dissertation, it is recommended that the dissertation be viewed in colour.
